---
title: "Processing anemometer data"
output:
  html_notebook:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r}
library(readxl)
library(dygraphs)
library(ggplot2)
library(xts)
```

Testing out looking at the wind data from 2 anemometers deployed for a few days in ND and QB. QB sensor ends in 493, ND sensor ends in 505.

```{r}
filepath <- "../Delmarva/data/wind"
files <- list.files(filepath, full.names = TRUE)
```

Read in QB wind data from "Processed Records sheet" without the first 2 rows. Rename columns to avoid the special characters

```{r}
windcolnames <- c("Timestamp", "Wind_direction_degree", "wind_speed_metersPerSecond", "gust_speed_metersPerSecond", "anemometer_temp_degreeC")

qbwind <- readxl::read_xlsx(files[1], 
                            sheet = "Processed Records", 
                            skip = 3, 
                            col_names = windcolnames,
                            na = "#N/A",
                            col_types = c("date", rep("numeric", 4)))

ndwind <- readxl::read_xlsx(files[2], 
                            sheet = "Processed Records", 
                            skip = 3, 
                            col_names = windcolnames,
                            na = "#N/A",
                            col_types = c("date", rep("numeric", 4)))

```

Plot with suggested deployment cut off times

```{r}
ggplot(qbwind, aes(x = Timestamp, y = wind_speed_metersPerSecond)) +
  geom_line(col = "blue") +
  # geom_point(col = "blue", size = 1, pch = 1, aes(x = Timestamp, y = gust_speed_metersPerSecond)) +
  geom_line(data = ndwind, col = "orange") +
  # geom_point(data = ndwind, col = "orange", size = 1, pch = 1, aes(x = Timestamp, y = gust_speed_metersPerSecond)) +
  theme_bw()

```

Gusts
```{r}

ggplot(qbwind, aes(x = Timestamp, y = wind_speed_metersPerSecond)) +
  # geom_line(col = "blue") +
  geom_point(col = "blue", size = 1, pch = 1, aes(x = Timestamp, y = gust_speed_metersPerSecond)) +
  # geom_line(data = ndwind, col = "orange") +
  geom_point(data = ndwind, col = "orange", size = 1, pch = 1, aes(x = Timestamp, y = gust_speed_metersPerSecond)) +
  theme_bw()
```

Dygraphs interactive plot

Combine data frames
```{r}
ndwind$site <- "ND"
qbwind$site <- "QB"
df <- rbind(ndwind, qbwind)

df_spread <- df %>% 
  dplyr::select(Timestamp, site, wind_speed_metersPerSecond) %>%
  tidyr::spread(key = site, value = wind_speed_metersPerSecond)
df_xts <- xts(df_spread[-1], order.by = df_spread$Timestamp)

df_spread_direction <- df %>% 
  dplyr::select(Timestamp, site, Wind_direction_degree) %>%
  tidyr::spread(key = site, value = Wind_direction_degree)
# df_xts <- xts(df_spread_direction[-1], order.by = df_spread$Timestamp)
```

```{r}
dygraph(df_xts) %>%
  dyRangeSelector() %>%
  dyLegend() %>%
  dyOptions(strokeWidth = 1.5) %>%
  dyRoller(rollPeriod = 5) %>% # plotted point represents average of specified number of timestamps
  dyAxis("y", label = "wind speed (m/s)")
```

wind rose for direction

